Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
general updates2

 Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are
 characteristic of various types of molecules and their interactions. It’s hard to calculate energies to make such landscapes - Professor of Physics
 Dan Browne at University College London proposed that although VQE has a much simpler quantum circuit it still uses a classical search as part of
 the process to find these molecular energies. “VQE will only work If you have prior knowledge - this helps to refine the search. In the search, you
 need to look in the right place.” He also commented “one could try combining both methods to make a better algorithm”. Could combining PEA and VQE
 conjure up a huge amount of benefits so much that it reduces flaws such as noise and error intolerance?

@@

 Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
 are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage quantum devices, and this paper by O’Malley et al.
 represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a promising validation of the
  development of superconducting qubits for scalable quantum hardware". And it certainly heralds an interesting future for the use both of
  superconducting qubits and variational quantum algorithms for tackling classically intractable problems in quantum chemistry and beyond.

>>>>

 Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are
 characteristic of various types of molecules and their interactions. It’s hard to calculate energies to make such landscapes - Professor of Physics
 Dan Browne at University College London proposed that although VQE has a much simpler quantum circuit it still uses a classical search as part of
 the process to find these molecular energies. ``VQE will only work If you have prior knowledge - this helps to refine the search. In the search, you
 need to look in the right place.” He also commented “one could try combining both methods to make a better algorithm”. Could combining PEA and VQE
 conjure up a huge amount of benefits so much that it reduces flaws such as noise and error intolerance?

@@

 Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that ``variational techniques in quantum chemistry
 are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage quantum devices, and this paper by O’Malley et al.
 represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a promising validation of the
  development of superconducting qubits for scalable quantum hardware". And it certainly heralds an interesting future for the use both of
  superconducting qubits and variational quantum algorithms for tackling classically intractable problems in quantum chemistry and beyond.
